### 2017-03-09 Document/LaTeX/ArticleExample.tex
ENH:  INitial commit.

%
% Complete documentation on the extended LaTeX markup used for Insight
% documentation is available in ``Documenting Insight'', which is part
% of the standard documentation for Insight.  It may be found online
% at:
%
%     http://www.itk.org/

\documentclass{InsightArticle}

\usepackage[dvips]{graphicx}
\usepackage[cmtip,all]{xy}
\newcommand{\longsquiggly}{\xymatrix{{}\ar@{~>}[r]&{}}}
\usepackage{mathtools}
\usepackage{subcaption}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}

%  This is a template for Papers to the Insight Journal.
%  It is comparable to a technical report format.

% The title should be descriptive enough for people to be able to find
% the relevant document.
\title{Two Luis Miguel fans walk into a bar in Nagoya $\xRightarrow[]{yada\,\,\,yada\,\,\,yada}$
an ITK-implementation of a popular patch-based denoising filter}

%
% NOTE: This is the last number of the "handle" URL that
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{3564}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.00}

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Nick Tustison$^{1}$ and Jose Vicente Manj\'on$^{2}$}
\authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
               $^{2}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
               }

\begin{document}

%
% Add hyperlink to the web location and license of the paper.
% The argument of this command is the handler identifier given
% by the Insight Journal to this paper.
%
\IJhandlefooter{\IJhandlerIDnumber}

%\ifpdf
%\else
%   %
%   % Commands for including Graphics when using latex
%   %
%   \DeclareGraphicsExtensions{.eps,.jpg,.gif,.tiff,.bmp,.png}
%   \DeclareGraphicsRule{.jpg}{eps}{.jpg.bb}{`convert #1 eps:-}
%   \DeclareGraphicsRule{.gif}{eps}{.gif.bb}{`convert #1 eps:-}
%   \DeclareGraphicsRule{.tiff}{eps}{.tiff.bb}{`convert #1 eps:-}
%   \DeclareGraphicsRule{.bmp}{eps}{.bmp.bb}{`convert #1 eps:-}
%   \DeclareGraphicsRule{.png}{eps}{.png.bb}{`convert #1 eps:-}
%\fi

\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\begin{abstract}
\noindent
This document describes an ITK implementation of the adaptive patch-based
image denoising algorithm described in \cite{Manjon:2010aa}.  This offering consists
of the templated class itkPatchBasedDenoisingImageFilter interfaced through
the DenoiseImage program which includes its own interface program.  We include
a couple of examples.
\end{abstract}

\IJhandlenote{\IJhandlerIDnumber}

% \tableofcontents

\section{Introduction}

Image filtering techniques are usually applied to increase the quality of MR images.
Most of these techniques assume an equal noise distribution across the image. When this
assumption is not met, the resulting filtering becomes suboptimal. This is the case of MR
images with spatially varying noise levels, such as those obtained by parallel imaging
(sensitivity-encoded), intensity inhomogeneity-corrected images or surface coil based
acquisitions. In this work, we have adapted a recently proposed filter so-called
Non-Local Means (NL-means) to deal with MR images with spatially varying noise levels
(for both Gaussian and Rician distributed noise). With this new method, information
regarding the local image noise level is used to adjust the amount of denoising strength
of the filter. Such information is automatically obtained from the images by using the
local noise estimation method described in \cite{Manjon:2010aa}.

This method has been validated and compared with the standard NL-means filter on simulated
and real MR imaging data. This noise-adaptive NL-means method was demonstrated to outperform
the standard NL-means based filter when spatially varying noise is present in the images.
Although source code is available from Prof. Manj\'on Herrera's website
(http://personales.upv.es/jmanjon/denoising/arnlm.html).  This particular algorithm is
currently not available in the Insight Toolkit which provides good performance with minimal
parameter tuning. In this Insight Journal submission, we provide a brief overview of the ITK
implementation and provide a couple examples.

\section{ITK Implementation}

The following files define the adaptive NL-means algorithm and is written in ITK
coding style:
\begin{itemize}
  \item itkAdaptiveNonLocalMeansDenoisingImageFilter.h
  \item itkAdaptiveNonLocalMeansDenoisingImageFilter.hxx
\end{itemize}
The following helper class
\begin{itemize}
  \item itkVarianceImageFilter.h
  \item itkVarianceImageFilter.hxx
\end{itemize}
is the variance analog to the \doxygen{MeanImageFilter} which ``Computes an image where a
given pixel is the [variance] value of the the pixels in a neighborhood about the corresponding
input pixel.''  Both the adaptive and variance filters are multi-threaded.

Additionally, we wrote an easy-to-use interface program, DenoiseImage.cxx, with an ANTs-based command
line interface facilitated by the following helper classes:
\begin{itemize}
  \item antsCommandLineOption.h
  \item antsCommandLineOption.cxx
  \item antsCommandLineParser.h
  \item antsCommandLineParser.cxx
\end{itemize}
These latter files are not essential for other applications or for inclusion into ITK.
They are included simply to facilitate the generation of a stand-alone application that
people can use.  One can invoke the help menu via \verb#$ DenoiseImage --help 1# at the
command line:
\small
\begin{verbatim}
$ DenoiseImage --help 1

COMMAND:
     DenoiseImage
          Denoise an image using a spatially adaptive filter originally described in J. V.
          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.

OPTIONS:
     -d, --image-dimensionality 2/3/4
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, the program tries to infer the dimensionality from the input
          image.

     -i, --input-image inputImageFilename
          A scalar image is expected as input for noise correction.

     -n, --noise-model Rician/(Gaussian)
          Employ a Rician or Gaussian noise model.

     -x, --mask-image maskImageFilename
          If a mask image is specified, denoising is only performed in the mask region.

     -s, --shrink-factor (1)/2/3/...
          Running noise correction on large images can be time consuming. To lessen
          computation time, the input image can be resampled. The shrink factor, specified
          as a single integer, describes this resampling. Shrink factor = 1 is the
          default.

     -p, --patch-radius 1
                        1x1x1
          Patch radius. Default = 1x1x1

     -r, --search-radius 3
                         3x3x3
          Search radius. Default = 3x3x3.

     -o, --output correctedImage
                  [correctedImage,<noiseImage>]
          The output consists of the noise corrected version of the input image.
          Optionally, one can also output the estimated noise image.

     -v, --verbose (0)/1
          Verbose output.

     -h
          Print the help menu (short version).

     --help
          Print the help menu.
\end{verbatim}
\normalsize
which should provide minimal detail regarding each parameter.  The default parameters
should provide adequate performance for a variety of cases thus requiring only the simple
call (for a 3-D image)

\small
\begin{verbatim}
$ DenoiseImage -d 3 -i ${inputImage} -o ${outputImage}
\end{verbatim}
\normalsize

As mentioned, this filter is multi-threaded so one might want to set the environment
variable to enable more than one thread, e.g.,
\small
\begin{verbatim}
$ export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=4
\end{verbatim}
\normalsize

To see the progress of the filter, one also needs to set the verbose flag, i.e.,
\verb#-v 1#.

\section{Examples}

We included a 2-D brain slice and a 3-D hyperpolarized gas volume each with a corresponding
mask.  Below we include the call and resulting output for these two sets of data.

\subsection{T1-weighted MRI brain slice}

\small
\begin{verbatim}
$ DenoiseImage -d 2 -i t81slice.nii.gz -x t81mask.nii.gz -o t81denoised.nii.gz -v 1

Running for 2-dimensional images.

*********10*********20*********30*********40*********50*********60*********70*********80*********90*********

   AdaptiveNonLocalMeansDenoisingImageFilter (0x7f9733997080)
     RTTI typeinfo:   itk::AdaptiveNonLocalMeansDenoisingImageFilter<itk::Image<float, 2u>, itk::Image<float, 2u>, itk::Image<unsigned char, 2u> >
     Reference Count: 1
     Modified Time: 517
     Debug: Off
     Object Name:
     Observers:
       ProgressEvent(Command)
     Inputs:
       Primary: (0x7f9733996c10) *
       _1: (0x7f97339988f0)
     Indexed Inputs:
       0: Primary (0x7f9733996c10)
       1: _1 (0x7f97339988f0)
     Required Input Names: Primary
     NumberOfRequiredInputs: 1
     Outputs:
       Primary: (0x7f9733996a50)
     Indexed Outputs:
       0: Primary (0x7f9733996a50)
     NumberOfRequiredOutputs: 1
     Number Of Threads: 1
     ReleaseDataFlag: Off
     ReleaseDataBeforeUpdateFlag: Off
     AbortGenerateData: Off
     Progress: 1
     Multithreader:
       RTTI typeinfo:   itk::MultiThreader
       Reference Count: 1
       Modified Time: 299
       Debug: Off
       Object Name:
       Observers:
         none
       Thread Count: 1
       Global Maximum Number Of Threads: 128
       Global Default Number Of Threads: 1
     CoordinateTolerance: 1e-06
     DirectionTolerance: 1e-06
     Using Gaussian noise model.
     Epsilon = 1e-05
     Mean threshold = 0.95
     Variance threshold = 0.5
     Smoothing variance = 2
     Neighborhood radius for local mean and variance = [1, 1]
     Neighborhood search radius  = [3, 3]
     Neighborhood block radius = [1, 1]
Elapsed time: 0.0831451
\end{verbatim}
\normalsize

\begin{figure}[!ht]
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/t81slice.eps}
  \caption{Original}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/t81denoised.eps}
  \caption{Denoised}
\end{subfigure}
\caption{Effects of the NL-means filter on a 2-D T1-weighted MRI brain slice.}
\end{figure}

\subsection{Hyperpolarized He3 Lung MRI volume}

\small
\begin{verbatim}
$ DenoiseImage -d 3 -i he3volume.nii.gz -x he3mask.nii.gz -o he3denoised.nii.gz -v 1

Running for 3-dimensional images.

*********10*********20*********30*********40*********50*********60*********70*********80*********90*********

   AdaptiveNonLocalMeansDenoisingImageFilter (0x7ff279e0a440)
     RTTI typeinfo:   itk::AdaptiveNonLocalMeansDenoisingImageFilter<itk::Image<float, 3u>, itk::Image<float, 3u>, itk::Image<unsigned char, 3u> >
     Reference Count: 1
     Modified Time: 506
     Debug: Off
     Object Name:
     Observers:
       ProgressEvent(Command)
     Inputs:
       Primary: (0x7ff27a97ea20) *
       _1: (0x7ff27a97f040)
     Indexed Inputs:
       0: Primary (0x7ff27a97ea20)
       1: _1 (0x7ff27a97f040)
     Required Input Names: Primary
     NumberOfRequiredInputs: 1
     Outputs:
       Primary: (0x7ff279e0a710)
     Indexed Outputs:
       0: Primary (0x7ff279e0a710)
     NumberOfRequiredOutputs: 1
     Number Of Threads: 4
     ReleaseDataFlag: Off
     ReleaseDataBeforeUpdateFlag: Off
     AbortGenerateData: Off
     Progress: 1
     Multithreader:
       RTTI typeinfo:   itk::MultiThreader
       Reference Count: 1
       Modified Time: 294
       Debug: Off
       Object Name:
       Observers:
         none
       Thread Count: 4
       Global Maximum Number Of Threads: 128
       Global Default Number Of Threads: 4
     CoordinateTolerance: 1e-06
     DirectionTolerance: 1e-06
     Using Gaussian noise model.
     Epsilon = 1e-05
     Mean threshold = 0.95
     Variance threshold = 0.5
     Smoothing variance = 2
     Neighborhood radius for local mean and variance = [1, 1, 1]
     Neighborhood search radius  = [3, 3, 3]
     Neighborhood block radius = [1, 1, 1]
Elapsed time: 1.7134
\end{verbatim}
\normalsize

\begin{figure}[!ht]
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/he3volume.eps}
  \caption{Original}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/he3denoised.eps}
  \caption{Denoised}
\end{subfigure}
\caption{Effects of the NL-means filter on a 3-D hyperpolarized gas MRI lung volume.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Insert the bibliography using BibTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
\bibliography{InsightJournal}

\end{document}

### 2017-03-09 Source/itkAdaptiveNonLocalMeansDenoisingImageFilter.h

@@ -1,0 +1,209 @@
+/*=========================================================================
+ *
+ *  Copyright Insight Software Consortium
+ *
+ *  Licensed under the Apache License, Version 2.0 (the "License");
+ *  you may not use this file except in compliance with the License.
+ *  You may obtain a copy of the License at
+ *
+ *         http://www.apache.org/licenses/LICENSE-2.0.txt
+ *
+ *  Unless required by applicable law or agreed to in writing, software
+ *  distributed under the License is distributed on an "AS IS" BASIS,
+ *  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ *  See the License for the specific language governing permissions and
+ *  limitations under the License.
+ *
+ *=========================================================================*/
+#ifndef itkAdaptiveNonLocalMeansDenoisingImageFilter_h
+#define itkAdaptiveNonLocalMeansDenoisingImageFilter_h
+
+#include "itkNonLocalPatchBasedImageFilter.h"
+
+#include "itkConstNeighborhoodIterator.h"
+#include "itkGaussianOperator.h"
+
+namespace itk {
+
+/**
+ * \class AdaptiveNonLocalMeansDenoisingImageFilter
+ * \brief Implementation of a denoising image filter.
+ *
+ * \author Jose V. Manjon with ITK porting by Nick Tustison
+ *
+ * Contributed by
+ *
+ * \par REFERENCE
+ *
+ * J. V. Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins,
+ * and M. Robles. "Adaptive Non-Local Means Denoising of MR Images With
+ * Spatially Varying Noise Levels, Journal of Magnetic Resonance Imaging,
+ * 31:192-203, June 2010.
+ *
+ * \ingroup ITKNoiseFiltering
+ */
+
+template<typename TInputImage,
+  typename TOutputImage = TInputImage,
+  typename TMaskImage = Image<unsigned char, TInputImage::ImageDimension> >
+class AdaptiveNonLocalMeansDenoisingImageFilter :
+  public NonLocalPatchBasedImageFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef AdaptiveNonLocalMeansDenoisingImageFilter                 Self;
+  typedef NonLocalPatchBasedImageFilter<TInputImage, TOutputImage>  Superclass;
+  typedef SmartPointer<Self>                                        Pointer;
[…]

### 2017-03-09 Source/itkNonLocalSuperresolutionImageFilter.h

@@ -1,0 +1,228 @@
+/*=========================================================================
+ *
+ *  Copyright Insight Software Consortium
+ *
+ *  Licensed under the Apache License, Version 2.0 (the "License");
+ *  you may not use this file except in compliance with the License.
+ *  You may obtain a copy of the License at
+ *
+ *         http://www.apache.org/licenses/LICENSE-2.0.txt
+ *
+ *  Unless required by applicable law or agreed to in writing, software
+ *  distributed under the License is distributed on an "AS IS" BASIS,
+ *  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ *  See the License for the specific language governing permissions and
+ *  limitations under the License.
+ *
+ *=========================================================================*/
+#ifndef itkNonLocalSuperresolutionImageFilter_h
+#define itkNonLocalSuperresolutionImageFilter_h
+
+#include "itkNonLocalPatchBasedImageFilter.h"
+
+#include "itkConstNeighborhoodIterator.h"
+
+namespace itk {
+
+/**
+ * \class NonLocalSuperresolutionImageFilter
+ * \brief Implementation of a non-local upsampling (i.e., superresolution) image filter.
+ *
+ * \author Jose V. Manjon with ITK porting by Nick Tustison
+ *
+ * Contributed by
+ *
+ * \par REFERENCE
+ *
+ * José V. Manjón, Pierrick Coupe, Antonio Buades, Vladimir Fonov, Louis Collins and
+ * Montserrat Robles.
+ * "Non-local MRI Upsampling",
+ * Medical Image Analysis, 14:784-792, 2010.
+ *
+ * José V. Manjón, Pierrick Coupe, Antonio Buades, Louis Collins and Montserrat Robles.
+ * "MRI Superresolution Using Self-Similarity and Image Priors",
+ * International Journal of Biomedical Imaging, 2010.
+ *
+ * \ingroup ITKFiltering
+ */
+
+template<typename TInputImage, class TOutputImage = TInputImage>
+class NonLocalSuperresolutionImageFilter :
+  public NonLocalPatchBasedImageFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef NonLocalSuperresolutionImageFilter                         Self;
+  typedef NonLocalPatchBasedImageFilter<TInputImage, TOutputImage>   Superclass;
+  typedef SmartPointer<Self>                                         Pointer;
[…]

### 2017-03-09 Source/itkWeightedVotingFusionImageFilter.h

@@ -1,0 +1,395 @@
+/*=========================================================================
+ *
+ *  Copyright Insight Software Consortium
+ *
+ *  Licensed under the Apache License, Version 2.0 (the "License");
+ *  you may not use this file except in compliance with the License.
+ *  You may obtain a copy of the License at
+ *
+ *         http://www.apache.org/licenses/LICENSE-2.0.txt
+ *
+ *  Unless required by applicable law or agreed to in writing, software
+ *  distributed under the License is distributed on an "AS IS" BASIS,
+ *  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ *  See the License for the specific language governing permissions and
+ *  limitations under the License.
+ *
+ *=========================================================================*/
+#ifndef __itkWeightedVotingFusionImageFilter_h
+#define __itkWeightedVotingFusionImageFilter_h
+
+#include "itkNonLocalPatchBasedImageFilter.h"
+
+#include "itkImageRegionIterator.h"
+#include "itkImageRegionConstIterator.h"
+#include "itkConstNeighborhoodIterator.h"
+
+#include <vnl/vnl_matrix.h>
+#include <vnl/vnl_vector.h>
+
+#include <vector>
+#include <map>
+#include <set>
+
+namespace itk
+{
+
+/** \class WeightedVotingFusionImageFilter
+ * \brief Implementation of the joint label fusion and joint intensity fusion algorithm
+ *
+ * \author Paul Yushkevich with modifications by Brian Avants and Nick Tustison
+ *
+ * \par REFERENCE
+ *
+ * H. Wang, J. W. Suh, S. Das, J. Pluta, C. Craige, P. Yushkevich,
+ * "Multi-atlas segmentation with joint label fusion," IEEE Trans.
+ * on Pattern Analysis and Machine Intelligence, 35(3), 611-623, 2013.
+ *
+ * H. Wang and P. A. Yushkevich, "Multi-atlas segmentation with joint
+ * label fusion and corrective learning--an open source implementation,"
+ * Front. Neuroinform., 2013.
+ *
+ * \ingroup ImageSegmentation
+ */
+
+template <class TInputImage, class TOutputImage>
+class WeightedVotingFusionImageFilter
+: public NonLocalPatchBasedImageFilter<TInputImage, TOutputImage>
+{
+public:
+  /** Standard class typedefs. */
+  typedef WeightedVotingFusionImageFilter                            Self;
[…]

### 2017-03-13 Document/LaTeX/ArticleExample.tex
ENH:  Refactoring.

@@
 % the relevant document.
-\title{Two Luis Miguel fans walk into a bar in Nagoya $\xRightarrow[]{yada\,\,\,yada\,\,\,yada}$
-an ITK-implementation of a popular patch-based denoising filter}
+\title{A patch-based framework for new ITK functionality:  Joint fusion, denoising,
+and non-local super-resolution}
 
@@
 %
-\newcommand{\IJhandlerIDnumber}{3564}
+\newcommand{\IJhandlerIDnumber}{}
 
@@
 % snail-mail address if you like.
-\author{Nick Tustison$^{1}$ and Jose Vicente Manj\'on$^{2}$}
+\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Long Xie$^{3}$, Paul Yushkevich$^{3}$, and Jose Vicente Manj\'on$^{4}$}
 \authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
-               $^{2}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
+               $^{2}$Biogen, Cambridge, MA\\
+               $^{3}$University of Pennsylviania, Philadelphia, PA\\
+               $^{4}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
                }
@@
 \noindent
-This document describes an ITK implementation of the adaptive patch-based
-image denoising algorithm described in \cite{Manjon:2010aa}.  This offering consists
-of the templated class itkPatchBasedDenoisingImageFilter interfaced through
-the DenoiseImage program which includes its own interface program.  We include
-a couple of examples.
+In an earlier Insight Journal article, we introduced an ITK implementation of the
+adaptive patch-based image denoising algorithm described in \cite{Manjon:2010aa}.
+We follow-up up that offering with a generalized non-local, patch-based ITK class
+framework and a refactored denoising class.  In addition, we provide two additional
+ITK implementations of related, well-known algorithms.  The first is a non-local
+super resolution method described in \cite{Manjon:2010ab,Manjon:2010ac}.  The second is
+the multivariate
+joint label fusion algorithm of \cite{Wang:2013ab,Wang:2013aa}.  Accompanying these ITK classes are
+documented programming interfaces which use our previously introduced unique
+command line interface routines.  Several 2-D examples on brain imaging data are
+provided to qualitatively demonstrate performance.
 \end{abstract}

### 2017-03-15 Document/LaTeX/ArticleExample.tex
ENH:  UPdate text.

@@
 % snail-mail address if you like.
-\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Long Xie$^{3}$, Paul Yushkevich$^{3}$, and Jose Vicente Manj\'on$^{4}$}
+\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Hongzhi Wang$^{3}$, Long Xie$^{4}$, Paul Yushkevich$^{4}$, and Jose Vicente Manj\'on$^{5}$}
 \authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
                $^{2}$Biogen, Cambridge, MA\\
-               $^{3}$University of Pennsylviania, Philadelphia, PA\\
-               $^{4}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
+               $^{3}$IBM, San Jose, CA\\
+               $^{4}$University of Pennsylviania, Philadelphia, PA\\
+               $^{5}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
                }
@@
 We follow-up up that offering with a generalized non-local, patch-based ITK class
-framework and a refactored denoising class.  In addition, we provide two additional
+framework and a refactored denoising class.  In addition, we provide two
 ITK implementations of related, well-known algorithms.  The first is a non-local
@@
 the multivariate
-joint label fusion algorithm of \cite{Wang:2013ab,Wang:2013aa}.  Accompanying these ITK classes are
+joint label fusion algorithm of \cite{Wang:2013ab,Wang:2013aa} with additional extensions,
+denoted as ``joint intensity fusion'', which will be described in a forthcoming manuscript.
+Accompanying these ITK classes are
 documented programming interfaces which use our previously introduced unique
@@
 
-Image filtering techniques are usually applied to increase the quality of MR images.
-Most of these techniques assume an equal noise distribution across the image. When this
-assumption is not met, the resulting filtering becomes suboptimal. This is the case of MR
-images with spatially varying noise levels, such as those obtained by parallel imaging
-(sensitivity-encoded), intensity inhomogeneity-corrected images or surface coil based
-acquisitions. In this work, we have adapted a recently proposed filter so-called
-Non-Local Means (NL-means) to deal with MR images with spatially varying noise levels
-(for both Gaussian and Rician distributed noise). With this new method, information
-regarding the local image noise level is used to adjust the amount of denoising strength
-of the filter. Such information is automatically obtained from the images by using the
-local noise estimation method described in \cite{Manjon:2010aa}.
-
-This method has been validated and compared with the standard NL-means filter on simulated
-and real MR imaging data. This noise-adaptive NL-means method was demonstrated to outperform
-the standard NL-means based filter when spatially varying noise is present in the images.
-Although source code is available from Prof. Manj\'on Herrera's website
-(http://personales.upv.es/jmanjon/denoising/arnlm.html).  This particular algorithm is
-currently not available in the Insight Toolkit which provides good performance with minimal
-parameter tuning. In this Insight Journal submission, we provide a brief overview of the ITK
-implementation and provide a couple examples.
+Since the non-local (NL) means algorithm introduced in several early papers \cite{Buades},
+the resulting family of research techniques has grown to significant prominence within the
+medical imaging community.  In addition to continued research output, patch-based techniques
+have been the subject of workshops (Patch-MI 2015 and PMI'16, both MICCAI-sponsored
+workshops).   Given the interest and potential applications, this submission is a potential
+``conversation starter'' for the development of an ITK software framework
 

### 2017-03-15 Document/LaTeX/ArticleExample.tex
ENH:  Add author.

@@
 % snail-mail address if you like.
-\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Hongzhi Wang$^{3}$, Long Xie$^{4}$, Paul Yushkevich$^{4}$, and Jose Vicente Manj\'on$^{5}$}
-\authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
-               $^{2}$Biogen, Cambridge, MA\\
-               $^{3}$IBM, San Jose, CA\\
-               $^{4}$University of Pennsylviania, Philadelphia, PA\\
-               $^{5}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
+\author{Nick Tustison$^{1}$
+        Brian Avants$^{2}$,
+        Hongzhi Wang$^{3}$,
+        Long Xie$^{5}$,
+        Pierrick Coup\'e$^{4}$,
+        Paul Yushkevich$^{5}$, and
+        Jose Vicente Manj\'on$^{5}$}
+\authoraddress{$^{1}$University of Virginia, Charlottesville, VA, USA\\
+               $^{2}$Biogen, Cambridge, MA, USA\\
+               $^{3}$IBM Research, San Jose, CA, USA\\
+               $^{4}$ Laboratoire Bordelais de Recherche en Informatique, Talence, France\\
+               $^{5}$University of Pennsylviania, Philadelphia, USA\\
+               $^{6}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
                }
-
 \begin{document}
@@
 
-Since the non-local (NL) means algorithm introduced in several early papers \cite{Buades},
+Since the non-local (NL) means algorithm introduced in several early papers,
 the resulting family of research techniques has grown to significant prominence within the
@@
 workshops).   Given the interest and potential applications, this submission is a potential
-``conversation starter'' for the development of an ITK software framework
+``conversation starter'' for the development of an ITK software framework for accommodating
+such techniques.
 
@@
 
-The following files define the adaptive NL-means algorithm and is written in ITK
-coding style:
+\subsection{Parent and child classes}
+
+Based on the implementations of different algorithms from the various authors,
+the common routines were grouped to the following parent class:
+
+\begin{itemize}
+  \item itkNonLocalPatchBasedImageFilter.h
+  \item itkNonLocalPatchBasedImageFilter.hxx
+\end{itemize}
+
+The common routines contained within this class include defining both the
+patch and search neighborhoods.  We also define two patch similarity
+metrics---sum of squared differences (SSD) and Pearson's correlation.
+We also provide methods for ``vectorizing'' image patches and multiple image
+patches (for multi-modal applications) for facilitating similarity metric
+calculation.
+
+We provide the following classes for the adaptive denoising algorithm:
 \begin{itemize}
@@
 \end{itemize}
-is the variance analog to the \doxygen{MeanImageFilter} which ``Computes an image where a
+These have been refactored since our previous contribution such that the
+adaptive denoising class is derived from the parent class.  Again, the
+second class is the variance analog to the \doxygen{MeanImageFilter}
+which ``Computes an image where a
 given pixel is the [variance] value of the the pixels in a neighborhood about the corresponding
-input pixel.''  Both the adaptive and variance filters are multi-threaded.
+input pixel.''
 
-Additionally, we wrote an easy-to-use interface program, DenoiseImage.cxx, with an ANTs-based command
-line interface facilitated by the following helper classes:
+For the super-resolution algorithm, we provide the following class:
+\begin{itemize}
+  \item itkNonLocalSuperresolutionImageFilter.h
+  \item itkNonLocalSuperresolutionImageFilter.hxx
+\end{itemize}
+which subsumes functionalities described in both \cite{Manjon:2010ab,Manjon:2010ac}.
+
+Finally, for the joint fusion algorithm \cite{Wang:2013ab,Wang:2013aa} we provide
+the following class:
+\begin{itemize}
+  \item itkWeightedVotingFusionImageFilter.h
+  \item itkWeightedVotingFusionImageFilter.hxx
+\end{itemize}
+
+Note that all classes are multi-threaded.
+
+\subsection{Programs}
+
+We provide the following routines which use the above-listed classes:
+\begin{itemize}
+  \item DenoiseImage.cxx
+  \item NonLocalSuperResolution.cxx
+  \item jointFusion.cxx
+\end{itemize}
+
+All these routines use an ANTs-based command line interface facilitated by the
+following helper classes:
 \begin{itemize}
@@
 They are included simply to facilitate the generation of a stand-alone application that
-people can use.  One can invoke the help menu via \verb#$ DenoiseImage --help 1# at the
-command line:
+people can use.
+
+One can invoke the help menu for all these routines via the \verb#--help# option invoked at the
+command line.  To see the progress of the filter, one also needs to set the verbose flag, i.e.,
+\verb#-v 1#.  Below we give the help menu for each program.
+
+\subsection{Denoise image}
+
 \small
@@
 \normalsize
-which should provide minimal detail regarding each parameter.  The default parameters
-should provide adequate performance for a variety of cases thus requiring only the simple
-call (for a 3-D image)
+
+\subsection{Super-resolution}
 
@@
 \begin{verbatim}
-$ DenoiseImage -d 3 -i ${inputImage} -o ${outputImage}
+$ NonLocalSuperResolution --help 1
+
+COMMAND:
+     NonLocalSuperResolution
+          Non-local super resolution described in the following papers: 1) JV Manjon, P
+          Coupe, A Buades, V Fonov, DL Collins, and Montserrat Robles. Non-local MRI
+          Upsampling.Medical Image Analysis, 14:784-792, 2010 and2) JV Manjon, P Coupe, A
+          Buades, DL Collins, and Montserrat Robles. MRI Superresolution Using
+          Self-Similarity and Image Priors.International Journal of Biomedical Imaging,
+          2010.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -i, --input-image inputImageFilename
+          A low-resolution image input image to be superresoluted.
+
+     -j, --interpolated-image inputImageFilename
+          An interpolated version of the low-resolution image (such as B-spline). One
+          should specify either this option as a secondary input or a high-resolution
+          multi-modal counterpart (cf the -k option).
+
+     -k, --reference-image inputImageFilename
+          A high resolution reference multi-modal image. Assumed to be in the same space
+          as the low-resolution input image (i.e., registered).One should specify either
+          this option as a secondary input or an interpolated version (cf the -j option).
+
+     -p, --patch-radius 1
+                        1x1x1
+          Patch radius. Default = 1x1x1
+
+     -r, --search-radius 3
+                         3x3x3
+          Search radius. Default = 3x3x3.
+
+     -g, --intensity-difference-sigma 1.0
+          Intensity difference sigma. Default = 1.0
+
+     -t, --patch-similarity-sigma 1.0
+          Patch similarity sigma. Default = 1.0
+
+     -s, --scale-levels 32x16x8x2x1
+          Scale levels. Default = 32x16x8x2x1
+
+     -n, --interpolation Linear
+                         NearestNeighbor
+                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
+                         BSpline[<order=3>]
+                         CosineWindowedSinc
+                         WelchWindowedSinc
+                         HammingWindowedSinc
+                         LanczosWindowedSinc
+          Several interpolation options are available in ITK. These have all been made
+          available.
+
+     -o, --output outputImage
+          The output consists of the noise corrected version of the input image.
+          Optionally, one can also output the estimated noise image.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
 \end{verbatim}
@@
 
-As mentioned, this filter is multi-threaded so one might want to set the environment
-variable to enable more than one thread, e.g.,
+\subsection{Joint fusion}
+
 \small
 \begin{verbatim}
-$ export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=4
+$ jointFusion --help 1
+
+COMMAND:
+     antsJointFusion
+          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
+          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
+          original label fusion framework was extended to accommodate intensities by Brian
+          Avants. This implementation is based on Paul's original ITK-style implementation
+          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
+          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
+          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
+          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
+          with joint label fusion and corrective learning--an open source implementation,
+          Front. Neuroinform., 2013.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -t, --target-image targetImage
+                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
+          The target image (or multimodal target images) assumed to be aligned to a common
+          image domain.
+
+     -g, --atlas-image atlasImage
+                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
+          The atlas image (or multimodal atlas images) assumed to be aligned to a common
+          image domain.
+
+     -l, --atlas-segmentation atlasSegmentation
+          The atlas segmentation images. For performing label fusion the number of
+          specified segmentations should be identical to the number of atlas image sets.
+
+     -a, --alpha 0.1
+          Regularization term added to matrix Mx for calculating the inverse. Default =
+          0.1
+
+     -b, --beta 2.0
+          Exponent for mapping intensity difference to the joint error. Default = 2.0
+
+     -c, --constrain-nonnegative (0)/1
+          Constrain solution to non-negative weights.
+
+     -p, --patch-radius 2
+                        2x2x2
+          Patch radius for similarity measures. Default = 2x2x2
+
+     -m, --patch-metric (PC)/MSQ
+          Metric to be used in determining the most similar neighborhood patch. Options
+          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
+          correlation).
+
+     -s, --search-radius 3
+                         3x3x3
+                         searchRadiusMap.nii.gz
+          Search radius for similarity measures. Default = 3x3x3. One can also specify an
+          image where the value at the voxel specifies the isotropic search radius at that
+          voxel.
+
+     -e, --exclusion-image label[exclusionImage]
+          Specify an exclusion region for the given label.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, fusion is only performed in the mask region.
+
+     -o, --output labelFusionImage
+                  intensityFusionImageFileNameFormat
+                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
+          The output is the intensity and/or label fusion image. Additional optional
+          outputs include the label posterior probability images and the atlas voting
+          weight images.
+
+     --version
+          Get version information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
 \end{verbatim}
@@
 
-To see the progress of the filter, one also needs to set the verbose flag, i.e.,
-\verb#-v 1#.
+\section{Usage examples}
 
-\section{Examples}
+Instead of providing examples contained within the submission, we point to
+self-contained github repos which showcase usage for each of the three
+programs.
 
-We included a 2-D brain slice and a 3-D hyperpolarized gas volume each with a corresponding
-mask.  Below we include the call and resulting output for these two sets of data.
+\subsection{Denoise image}
 
-\subsection{T1-weighted MRI brain slice}
+\begin{itemize}
+  \item \url{https://github.com/ntustison/DenoiseImageExample}
+\end{itemize}
 
-\small
-\begin{verbatim}
-$ DenoiseImage -d 2 -i t81slice.nii.gz -x t81mask.nii.gz -o t81denoised.nii.gz -v 1
+\subsection{Super-resolution}
 
-Running for 2-dimensional images.
+\begin{itemize}
+  \item \url{https://github.com/ntustison/NonLocalSuperResolutionExample}
+\end{itemize}
 
-*********10*********20*********30*********40*********50*********60*********70*********80*********90*********
+\subsection{Joint fusion}
 
-   AdaptiveNonLocalMeansDenoisingImageFilter (0x7f9733997080)
-     RTTI typeinfo:   itk::AdaptiveNonLocalMeansDenoisingImageFilter<itk::Image<float, 2u>, itk::Image<float, 2u>, itk::Image<unsigned char, 2u> >
-     Reference Count: 1
-     Modified Time: 517
-     Debug: Off
-     Object Name:
-     Observers:
-       ProgressEvent(Command)
-     Inputs:
-       Primary: (0x7f9733996c10) *
-       _1: (0x7f97339988f0)
-     Indexed Inputs:
-       0: Primary (0x7f9733996c10)
-       1: _1 (0x7f97339988f0)
-     Required Input Names: Primary
-     NumberOfRequiredInputs: 1
-     Outputs:
-       Primary: (0x7f9733996a50)
-     Indexed Outputs:
-       0: Primary (0x7f9733996a50)
-     NumberOfRequiredOutputs: 1
-     Number Of Threads: 1
-     ReleaseDataFlag: Off
-     ReleaseDataBeforeUpdateFlag: Off
-     AbortGenerateData: Off
-     Progress: 1
-     Multithreader:
-       RTTI typeinfo:   itk::MultiThreader
-       Reference Count: 1
-       Modified Time: 299
-       Debug: Off
-       Object Name:
-       Observers:
-         none
-       Thread Count: 1
-       Global Maximum Number Of Threads: 128
-       Global Default Number Of Threads: 1
-     CoordinateTolerance: 1e-06
-     DirectionTolerance: 1e-06
-     Using Gaussian noise model.
-     Epsilon = 1e-05
-     Mean threshold = 0.95
-     Variance threshold = 0.5
-     Smoothing variance = 2
-     Neighborhood radius for local mean and variance = [1, 1]
-     Neighborhood search radius  = [3, 3]
-     Neighborhood block radius = [1, 1]
-Elapsed time: 0.0831451
-\end{verbatim}
-\normalsize
+Note that for the following example, the user will need to replace ``antsJointFusion''
+with ``jointFusion'' due to some legacy issues in preparing this submission.
 
-\begin{figure}[!ht]
-\begin{subfigure}{0.5\textwidth}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/t81slice.eps}
-  \caption{Original}
-\end{subfigure}
-\begin{subfigure}{0.5\textwidth}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/t81denoised.eps}
-  \caption{Denoised}
-\end{subfigure}
-\caption{Effects of the NL-means filter on a 2-D T1-weighted MRI brain slice.}
-\end{figure}
-
-\subsection{Hyperpolarized He3 Lung MRI volume}
-
-\small
-\begin{verbatim}
-$ DenoiseImage -d 3 -i he3volume.nii.gz -x he3mask.nii.gz -o he3denoised.nii.gz -v 1
-
-Running for 3-dimensional images.
-
-*********10*********20*********30*********40*********50*********60*********70*********80*********90*********
-
-   AdaptiveNonLocalMeansDenoisingImageFilter (0x7ff279e0a440)
-     RTTI typeinfo:   itk::AdaptiveNonLocalMeansDenoisingImageFilter<itk::Image<float, 3u>, itk::Image<float, 3u>, itk::Image<unsigned char, 3u> >
-     Reference Count: 1
-     Modified Time: 506
-     Debug: Off
-     Object Name:
-     Observers:
-       ProgressEvent(Command)
-     Inputs:
-       Primary: (0x7ff27a97ea20) *
-       _1: (0x7ff27a97f040)
-     Indexed Inputs:
-       0: Primary (0x7ff27a97ea20)
-       1: _1 (0x7ff27a97f040)
-     Required Input Names: Primary
-     NumberOfRequiredInputs: 1
-     Outputs:
-       Primary: (0x7ff279e0a710)
-     Indexed Outputs:
-       0: Primary (0x7ff279e0a710)
-     NumberOfRequiredOutputs: 1
-     Number Of Threads: 4
-     ReleaseDataFlag: Off
-     ReleaseDataBeforeUpdateFlag: Off
-     AbortGenerateData: Off
-     Progress: 1
-     Multithreader:
-       RTTI typeinfo:   itk::MultiThreader
-       Reference Count: 1
-       Modified Time: 294
-       Debug: Off
-       Object Name:
-       Observers:
-         none
-       Thread Count: 4
-       Global Maximum Number Of Threads: 128
-       Global Default Number Of Threads: 4
-     CoordinateTolerance: 1e-06
-     DirectionTolerance: 1e-06
-     Using Gaussian noise model.
-     Epsilon = 1e-05
-     Mean threshold = 0.95
-     Variance threshold = 0.5
-     Smoothing variance = 2
-     Neighborhood radius for local mean and variance = [1, 1, 1]
-     Neighborhood search radius  = [3, 3, 3]
-     Neighborhood block radius = [1, 1, 1]
-Elapsed time: 1.7134
-\end{verbatim}
-\normalsize
-
-\begin{figure}[!ht]
-\begin{subfigure}{0.5\textwidth}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/he3volume.eps}
-  \caption{Original}
-\end{subfigure}
-\begin{subfigure}{0.5\textwidth}
-  \centering
-  \includegraphics[width=0.8\linewidth]{Figures/he3denoised.eps}
-  \caption{Denoised}
-\end{subfigure}
-\caption{Effects of the NL-means filter on a 3-D hyperpolarized gas MRI lung volume.}
-\end{figure}
+\begin{itemize}
+  \item \url{https://github.com/ntustison/MalfLabelingExample}
+\end{itemize}
 

### 2017-05-31 Source/itkWeightedVotingFusionImageFilter.h
ENH:  Update code.

@@ -20,8 +20,6 @@
 
 #include "itkNonLocalPatchBasedImageFilter.h"
 
-#include "itkImageRegionIterator.h"
-#include "itkImageRegionConstIterator.h"
 #include "itkConstNeighborhoodIterator.h"
 
 #include <vnl/vnl_matrix.h>
